\tool: Revisiting BadUSB with Type-C

### 2021-03-05 WOOT/Files/related_work.tex
minor
Compare ours with JFC

@@

From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
are defined by the protocol to transmitting data. Without these pins, data cannot 
be transferred via a USB cable. Based
on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leaving power pins intact. However, this method poses
a great challenge to the plug-and-play property of USB, as once it is deployed, it
stops all USB functions other than charging.

>>>>

It is worth noting that our \tool is different from JFC~\cite{JFC}. Firstly, Juice Filming Attacks can not control the attacked device, but can only video-capture user inputs during charging. However, our \tool can monitor the screen at the same time as controling the attacked device, which enhances the efficiency of stealing users’ private data. Second, we design an prototype to attack in real time remotely. Third, the scope of \tool is wider, \tool also poses a threat to laptops that charged with use USB-C interface.

@@

From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a USB cable. Based
on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leaving power pins intact. However, this method poses
a great challenge to the plug-and-play property of USB, as once it is deployed, it
stops all USB functions other than charging.
